Models pretest

### 2022-12-08 Submission/Models_pretest.Rmd
new tests

@@

                                            location), "Amazonian Countries",

@@

                                          "Amazonian Countries",

@@

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small")
```

@@

>>>>

        py_1989=ifelse(grepl("1989", year), 1, 0),
        py_1992=ifelse(grepl("1992", year), 1, 0),
        py_2009=ifelse(grepl("2009", year), 1, 0),
        py_2015=ifelse(grepl("2015", year), 1, 0),
        py_2019=ifelse(grepl("2019", year), 1, 0),

@@

                                            location), "Amazonian States",

@@

@@

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small",
                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
                                             "Social Development", "National Sovereignty"),
                          covariate.labels = c("Speech outside Brazil", "Speech in Brasilia", "Speech in Non-amazonian Brazilian States", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
```

@@

```{r models president fixed effect w/ py, fig.cap="Fixed-effects logistic regressions by presidents with controls", echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, include=TRUE, results="asis"}

# model 3
c1 <- plm(con_vs_all ~ as.factor(location_cat) + 
                         def_year + AAI + election_year + py_1989+ py_1992+ py_2009+ py_2015+ py_2019,
                         data = ama_model_lag,
                         model = "within", index = "president")
c2 <- plm(EI_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + py_1989+py_1992+py_2009+py_2015+py_2019,
                         data = ama_model_lag,
                         model = "within", index = "president")
c3 <- plm(SD_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + py_1989+py_1992+py_2009+py_2015+py_2019,
                         data = ama_model_lag,
                         model = "within", index = "president")
c4 <- plm(sov_vs_all ~ as.factor(location_cat) +
                         def_year + AAI + election_year + py_1989+py_1992+py_2009+py_2015+py_2019,
                         data = ama_model_lag,
                         model = "within", index = "president")

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls and separate peak years",
                      column.sep.width = ".001pt",
                      font.size="small")
```
